---
title: ## `appler`
output: md_document
---

## `appler`

<!-- badges: start -->
[![R-CMD-check](https://github.com/ashbaldry/appler/workflows/R-CMD-check/badge.svg)](https://github.com/ashbaldry/appler/actions)
<!-- [![Codecov test coverage](https://codecov.io/gh/ashbaldry/appler/branch/main/graph/badge.svg)](https://codecov.io/gh/ashbaldry/appler?branch=main) -->
<!-- badges: end -->


The goal of `appler` is to be able to pull information from the Apple iTunes and App Stores.

### Installation

```{r, eval=FALSE}
devtools::install_github("ashbaldry/appler")
```

### Functionality

```{r}
library(appler)
```

#### `search_apple` 

A simple search tool that returns Apple items that are related to the search term.

```{r}
search_results <- search_apple("GitHub", "gb")
dim(search_results)
names(search_results)
```

#### `lookup_apple`

Using the ID of an Apple item (found in the URL) returns basic information about the selected item.

```{r}
lookup_results <- lookup_apple(1477376905, "gb")
dim(lookup_results)
names(lookup_results)
```

#### `get_apple_rating_split`

The API only extracts the average review, so this scrapes the app page for the split of 1 :star: to 5 :star: ratings.

```{r}
ratings <- get_apple_rating_split(1477376905, "gb")
ratings
```

#### `get_apple_reviews`

Pulls the most recent reviews for a selected app.

```{r}
reviews <- get_apple_reviews(1477376905, "gb")
head(reviews[-1, ])
```

#### `get_apple_chart_postion`

Checks whether the app is within any category chart and returns the postion and category

```{r}
chart_pos <- get_apple_chart_postion(1477376905, "gb")
chart_pos
```

__NB__ All ratings and reviews are country specific.
